Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{clclc}\hline
Pair & Community & Title & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P.Hall, et al. $2006$)      & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J.Fan, et al, $2004$)                       & \\
2    & VarSel      & The adaptive lasso and its oracle properties (H.Zou, $2006$)                             & \\
     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
3    & DimRed    & Contour projected dimension reduction (R.Luo, et al. $2009$)                                                     & \\
     & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
4    & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
     & DimRed    & Sliced regression for dimension reduction (H.Wang, et al. $2012$) & \\
5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J.Li, et al. $2012$)& \\
     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH.Zhang, et al. $2008$)        & \\
6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P.Hall, et al. $2010$)       & \\
     & CovEst     & Regularized estimation of large covariance matrices (PJ.Bickel, et al. $2008$)    &  \\
7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
     & VarSel     & Factor profiled sure independence screening (H.Wang, $2012$)    & \\
8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ.Yen, $2011$) & \\
     & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al, $2005$)                  & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
     (J.Fan, et al, $2011$)     & \\
10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
    (J.Fan, et al, $2010$) & \\
     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data  & \\
\hline
\end{tabular}
\caption{All the $10$ edges come from pairs of papers from different communities. For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. But they are not related in terms of topic.}
\end{table}
\label{tab:table2}
%\end{landscape}

@@

\begin{equation}
    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
    \frac{\delta}{2}\big\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
    \frac{3\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)
    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\gamma \big\|S^*_{M^\perp}\big\|_{1}
    \label{eq:11}
\end{equation}

>>>>

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{clclc}\hline
Pair & Community & Title (Author, Year) & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P.Hall, et al. $2006$)      & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J.Fan, et al, $2004$)                       & \\
2    & VarSel      & The adaptive lasso and its oracle properties (H.Zou, $2006$)                             & \\
     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
3    & DimRed    & Contour projected dimension reduction (R.Luo, et al. $2009$)                                                     & \\
     & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
4    & VarSel    & Factor profiled sure independence screening (H.Wang, $2012$)& \\
     & DimRed    & Sliced regression for dimension reduction (H.Wang, et al. $2012$) & \\
5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J.Li, et al. $2012$)& \\
     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH.Zhang, et al. $2008$)        & \\
6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P.Hall, et al. $2010$)       & \\
     & CovEst     & Regularized estimation of large covariance matrices (PJ.Bickel, et al. $2008$)    &  \\
7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
     & VarSel     & Factor profiled sure independence screening (H.Wang, $2012$)    & \\
8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ.Yen, $2011$) & \\
     & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
9    & Mixed    & Nonparametric inferences for additive models (J.Fan, et al. $2005$)                  & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
     (J.Fan, et al. $2011$)     & \\
10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
    (J.Fan, et al. $2010$) & \\
     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D.Zeng, et al. $2007$) & \\
\hline
\end{tabular}
\caption{All the $10$ edges come from pairs of papers from different communities. For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. But they are not related in terms of topic.}
\end{table}
\label{tab:table2}
%\end{landscape}

@@

\begin{equation}
    \frac{\tau}{2}\big\|\widehat{\Delta}^{\Theta}\big\|_{F}^{2} \leq
    \frac{\delta}{2}\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F} +
    \frac{3\delta}{2}\mathbb{Q}\big(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}\big)
    +2 \delta \sum_{j=k+1}^{n} \sigma_{j}\big(L^*\big) + 2\gamma \big\|S^*_{M^\perp}\big\|_{1}
    \label{eq:11}
\end{equation}
